Improved Smooth Free-Form Deformation with Sharp Feature Awareness

### 2016-08-10 paper.tex
add mobile platform in introduce
add something about mobile in relate work.

@@

Therefore, we propose a method which is based Smooth FFD to address the above problems.

>>>>

What's more, graphics applications is move to mobile platform due to the development of mobile hardware. So we also port our work on Android platform. It needs little addition effort thanks to the portable OpenGL.

@@

On the other hand, there're more and more graphic applications on the mobile platform. Mobile platform will develop so further that it not only show the 3D things, but also has the demand to edit the 3D model.\cite{mobile1}, \cite{mobile2} already do some work on mobile platform. We want to port a variant FFD method to mobile phone.

Therefore, we propose a method which is based Smooth FFD which can run on multi-platform including mobile platform to address the above problems.
